---
title: "hcic tools"
author: "André Calero Valdez"
output: 
  github_document:
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(corrplot)
library(hcictools)
```

## Package Contents
This is a package that contains helpful functions for survey data analysis. It is maintained by the Human-Computer Interaction Center at RWTH Aachen University.

## Installing the package

You can install this packages by running the following code.

```{r install, eval=FALSE, echo=TRUE}
  install.packages("devtools")
  library(devtools)
  devtools::install_github("HCIC/r-tools")
```

## Plotting Features

### Correlation Plots

```{r corplots, echot=TRUE, fig.width=5, fig.height=4}
a <- c(1,2,3,8,4,5,6,7)
b <- c(4,5,6,7,3,8,9,10)
d <- c(4,2,5,2,5,2,1,5)
df <- data.frame(a=a, b=b, d=d)

cor.matrix.plot(df)

```


### Confidence Interval Plots
It has a confidence interval plotting feature for indepedent sample tests.

```{r ci-plot, echo=TRUE}

plot_IS_meansCI(a, b)
```



## RWTH Palette
Drawing palettes and RWTH Corporate CI Colors
```{r corporate}

draw.palette(unlist( rwth.colorpalette() ))

```
## TBC
More to follow
