---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# hcictools

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/statisticsforsocialscience/hcictools/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/statisticsforsocialscience/hcictools/actions/workflows/R-CMD-check.yaml)
[![pkgdown](https://github.com/statisticsforsocialscience/hcictools/actions/workflows/pkgdown.yaml/badge.svg)](https://github.com/statisticsforsocialscience/hcictools/actions/workflows/pkgdown.yaml)
<!-- badges: end -->

The goal of hcictools is to make frequently recurring tasks in our work easier.

## Installation

You can install the released version of hcictools from [CRAN](https://CRAN.R-project.org) with:

``` r
# install.packages("remotes")
remotes::install_github("statisticsforsocialscience/hcictools")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(corrplot)
library(hcictools)
```

## Package Contents
This is a package that contains helpful functions for survey data analysis. It is maintained by the Human-Computer Interaction Center at RWTH Aachen University.

## Plotting Features

### Correlation Plots

```{r corplots, echot=TRUE, fig.width=5, fig.height=4}
a <- c(1,2,3,8,4,5,6,7)
b <- c(4,5,6,7,3,8,9,10)
d <- c(4,2,5,2,5,2,1,5)
df <- data.frame(a = a, b = b, d = d)

cor.matrix.plot(df)

```


### Confidence Interval Plots
It has a confidence interval plotting feature for indepedent sample tests.

```{r ci-plot, echo=TRUE}

plot_IS_meansCI(a, b)
```



## RWTH Palette
Drawing palettes and RWTH Corporate CI Colors
```{r corporate}

draw.palette(unlist( rwth.colorpalette() ))

```


## auto-code scale

Automatically extract item orientation and create mean score of items that have a prefix.

```{r}
newbfi <- psych::bfi %>% head(50) %>% auto_score("A")
```



## Careless indices

*Needs fixing*

```r
test_data <- tibble::tibble(
    ResponseId = 1:nrow(psych::bfi),
    `Duration (in seconds)` = stats::rnorm(nrow(psych::bfi), mean = 100, sd = 50),
    psych::bfi)


  careless_indices(test_data, 
                   duration_column = "Duration (in seconds)", 
                   id_column = "ResponseId", 
                   likert_vector = c(3:28)) %>% head()
```

## Extract plots from JMV models

```{r jmv_plot}
 jmv_result <- jmv::ANOVA(
    data = ToothGrowth,
    dep = "len",
    factors = c("supp", "dose"),
    emMeans = list(
      c("dose", "supp")))


  get_emm_plot(jmv_result) + ggplot2::labs(title = "test")
```



## TBC More to follow





